Generating exact lattices in a WFST framework

### 2011-09-26 misc/papers/icassp12_lat/paper.tex
Modified the introduction of the paper.
git-svn-id: https://svn.code.sf.net/p/kaldi/code/trunk@515 5e6a8d80-dfce-4ca6-a32a-6e07a63d50c8

\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother
\name{ Daniel Povey$^1$, Mirko Hannemann$^2$,  \\
  {Gilles Boulianne}$^3$, {Luk\'{a}\v{s} Burget}$^4$, {Arnab Ghoshal}$^5$, {Milos Janda}$^2$, {Stefan Kombrink}$^2$, \\
  {Petr Motl\'{i}\v{c}ek}$^6$, {Yanmin Qian}$^7$, {Ngoc Thang Vu}$^8$, {Korbinian Reidhammer}$^9$, {Karel Vesel\'{y}}$^2$
    \thanks{Thanks here}}
%\makeatletter
%\def\name#1{\gdef\@name{#1\\}}
%\makeatother

@@

The word ``lattice'' is used in the speech recognition literature to mean some
kind of compact representation of the most likely transcriptions of an utterance,
in the form of a graph structure and normally including score and alignment
information in addition to the word labels.  See 
for example~\cite{efficient_general,ney_word_graph,odell_thesis,saon2005anatomy}.

[more history + context here]

\section{Decoding with WFSTs}

@@

\section{Defining lattices and the lattice generation problem}

@@

\section{Previous lattice generation methods}

@@

\section{Overview of our algorithm}

@@

\section{Details of our $\epsilon$ removal and determinization algorithm}

>>>>

\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother
\name{ Daniel Povey$^1$, Mirko Hannemann$^{1,2}$,  \\
  {Gilles Boulianne}$^3$, {Luk\'{a}\v{s} Burget}$^4$, {Arnab Ghoshal}$^5$, {Milos Janda}$^2$, {Stefan Kombrink}$^2$, \\
  {Petr Motl\'{i}\v{c}ek}$^6$, {Yanmin Qian}$^7$, {Ngoc Thang Vu}$^8$, {Korbinian Reidhammer}$^9$, {Karel Vesel\'{y}}$^2$
    \thanks{Thanks here.. remember Sanjeev.}}
%\makeatletter
%\def\name#1{\gdef\@name{#1\\}}
%\makeatother

@@

In Section~\ref{sec:wfst} we give a Weighted Finite State Transducer
(WFST) interpretation of the speech-recognition decoding problem, in order
to introduce notation for the rest of the paper.  In Section~\ref{sec:lattices}
we define the lattice generation problem, and review previous work.
In Section~\ref{sec:overview} we give an overview of our method,
and in Section~\ref{sec:details} we summarize some aspects of a determinization
algorithm that we use in our method.  In Section~\ref{sec:exp} we give
experimental results, and in Section~\ref{sec:conc} we conclude.

\section{WFSTs and the decoding problem}
\label{sec:wfst}

@@

\section{The lattice generation problem, and previous work}
\label{sec:lattices}

\subsection{Lattices, and the lattice generation problem}

@@

\subsection{Previous lattice generation methods}

@@

\section{Overview of our algorithm}
\label{sec:overview}

@@

\section{Details of our $\epsilon$ removal and determinization algorithm}
\label{sec:details}
